Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-10 paper/tex/methods.tex
intro to ML redundancy

We test three publicly available and commonly used template-based codes, \lephare, \bpz, and \eazy, that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the \chisq\ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

@@

\subsection{Training-based Codes}
\label{sec:trainingcodes}

The training-based codes use a variety of algorithms in order to estimate $p(z)$, specifics of each implementation are described in the subsections.
Some aspects of data treatment were left to the individual code runners, for example, whether/how to split the available data with known redshifts into separate training and validation sets.
Another key difference is the treatment of non-detections in one or more bands.
Some codes choose to ignore a band, others replace the value with either an estimate for the detection limit, the mean of other values in the training set, or another default value.
There are varying conventions among training-based codes for treatment of non-detections, and no one prescription dominates in the photo-$z$ literature.
The specific choices for each code affect the results, and contribute to the implicit prior influencing their output.
However, we remind the reader that only 2.0 per cent of our sample has non-detections, almost exclusively in the u-band, and thus should not dominate the code performance differences.

@@

\textsc{ANNz2}\footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} is a software package that has the ability to employ several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree (BDT) and k-nearest neighbour (KNN).
Using the Toolkit for Multivariate Data Analysis (TMVA) with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, it can either run a single machine learning algorithm and return results, or it can run multiple algorithms simultaneously and output photo-$z$'s as a weighted combination of the different algorithms.
In this study, only ANNs were employed.
The redshift PDFs are produced by running an ensemble set of ANNs, each with different random seeds used in initialization of input parameters for training.
Uncertainties for each method are estimated from a KNN-uncertainty estimator \citep{Oyaizu:08}.
The final PDF can either be the ``best'' of the candidate PDFs, or a weighted average of the PDFs based on their error estimates for each of the ensemble members.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.  It can also perform classifications, and supports reweighting between samples.  The PDFs are produced by propagating the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

@@

\subsection{Simple Ensemble Estimator}\label{sec:method:trainz}

>>>>

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the \chisq\ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

@@

\subsection{Training-based Approaches}
\label{sec:trainingcodes}

We compared nine data-driven \pz\ estimation approaches, eight of which are described in this section and one of which is discussed in Section~\ref{sec:trainz}.
Because the algorithms differ more from one another and the techniques are relative newcomers to the astronomical literature, we provide somewhat more detail about the implementations below.
%
% Some aspects of data treatment were left to the individual code runners, for example, whether and how to split the DC1 training set for validation.
% The codes considered treated
% Another key difference is the treatment of non-detections in one or more bands.
% Some codes choose to ignore a band, others replace the value with either an estimate for the detection limit, the mean of other values in the training set, or another default value.
% There are varying conventions among training-based codes for treatment of non-detections, and no one prescription dominates in the photo-$z$ literature.
% The specific choices for each code affect the results, and contribute to the implicit prior influencing their output.
% However, we remind the reader that only 2.0 per cent of our sample has non-detections, almost exclusively in the u-band, and thus should not dominate the code performance differences.

@@

\annz \footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} employs several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree (BDT) and k-nearest neighbour (KNN).
Using the Toolkit for Multivariate Data Analysis (TMVA) with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, it can either run a single machine learning algorithm and return results, or it can run multiple algorithms simultaneously and output photo-$z$'s as a weighted combination of the different algorithms.
In this study, only ANNs were employed.
The redshift PDFs are produced by running an ensemble set of ANNs, each with different random seeds used in initialization of input parameters for training.
Uncertainties for each method are estimated from a KNN-uncertainty estimator \citep{Oyaizu:08}.
The final PDF can either be the ``best'' of the candidate PDFs, or a weighted average of the PDFs based on their error estimates for each of the ensemble members.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.  It can also perform classifications, and supports reweighting between samples.  The PDFs are produced by propagating the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

@@

\subsection{Simple Ensemble Estimator}
\label{sec:method:trainz}
